### 2020-04-02 probabilisticProgrammingMartingales.tex
minor

\lo{Ongoing}

@@

Overall, this implies that $\mathbb{E}[X_{n+1}] - \mathbb{E}[X_{n}] \leq -\mathbb P[M_{y_n} \text{not n.f.}]$ therefore as $\mathbb{E}[X_n]$ is bounded below, $\mathbb P[M_{y_n} \text{not n.f.}]$ must tend to 0 as $n \to \infty$. $M_{y_n} \text{n.f.} \Rightarrow M_{y_{n+1}} \text{n.f.}$ therefore 
\begin{align*}
\mathbb P[M_{y_n} \text{not n.f.~for infinitely many values of n}]  
& = \mathbb P[\forall n: M_{y_n} \text{not n.f.}] \\
& \leq \inf_n \mathbb P[M_{y_n} \text{not n.f.}] \\
& = 0
\end{align*} 
therefore $M$ terminates almost surely.
\end{proof}

>>>>

@@

Overall, this implies that $\mathbb{E}[X_{n+1}] - \mathbb{E}[X_{n}] \leq -\mathbb P[M_{y_n} \text{not n.f.}]$ therefore as $\mathbb{E}[X_n]$ is bounded below, $\mathbb P[M_{y_n} \text{not n.f.}]$ must tend to 0 as $n \to \infty$. $M_{y_n} \text{n.f.} \Rightarrow M_{y_{n+1}} \text{n.f.}$ therefore 
\begin{align*}
\mathbb P[M_{y_n} \text{not n.f.~for infinitely many values of $n$}]  
& = \mathbb P[\forall n: M_{y_n} \text{not n.f.}] \\
& \leq \inf_n \mathbb P[M_{y_n} \text{not n.f.}] \\
& = 0
\end{align*} 
therefore $M$ terminates almost surely.
\end{proof}
